Your Paper Title

### 2025-03-29 paper/paper.qmd
added first draft of intro/motivation and edited some citation

In this section, explain what drives you to consider this topic and why it is important.

@@

    The relationship between temperature and the flowering phenology of cherry blossoms (Prunus species, more commonly known as sakura) represents a unique merge of cultural heritage and biological science. For centuries, the timing of the sakura blooming has held profound cultural significance throughout East Asia, particularly in Japan, where the tradition of hanami (flower viewing) dates back to the Heian period. Beyond its cultural importance, the flowering phenology of sakura serves as a sensitive bioindicator of climate variability and change, with extensive historical records providing an exceptional opportunity to examine long-term temperature-phenology relationships [@Aono2008].

    This review examines the extensive body of literature addressing the correlation between temperature and sakura flowering dates, integrating perspectives from plant biology, phenological modeling, climatology, and cultural studies. The biological mechanisms underlying temperature sensitivity in cherry blossoms involve complex interactions between winter chilling requirements and early spring temperatures (Allen et al., 2014). Concurrently, the cultural documentation of flowering dates through imperial court diaries, temple records, and festival calendars has created one of the longest continuous biological datasets in existence, with some records from Kyoto extending back to 812 CE [@Aono2008].

>>>>

    The annual blooming of cherry blossoms (Prunus species, more commonly known as sakura) represents not only a culturally significant event across many East Asian countries but also serves as a valuable biological indicator of climate patterns and changes; particularly, the tradition of hanami (flower viewing) dates all the way back to the Heian period in Japan. This paper will examine the statistical relationship between temperature fluctuations and the timing of sakura flowering dates, a connection that has gained increased scientific attention as global climate change accelerates. Historical records of cherry blossom flowering, some dating back several centuries in Japan, provide an exceptionally rare long-term dataset for analyzing phenological responses to temperature variations [@Aono2008]. By quantifying this relationship through robust statistical methods, we aim to contribute to the growing body of research on biological responses to climate change while also contextualizing the potential cultural impacts of shifting bloom times. The preservation of these iconic natural events holds both scientific value for understanding ecosystem responses to warming trends and cultural significance for communities where cherry blossom festivals represent important economic and social traditions.

@@

    This literature review examines the extensive body of scholarly journals and articles addressing the correlation between temperature and sakura flowering dates, integrating perspectives from plant biology, phenological modeling, climatology, and cultural studies. The biological mechanisms underlying temperature sensitivity in cherry blossoms involve complex interactions between winter chilling requirements and early spring temperatures [@Allen2014]. Concurrently, the cultural documentation of flowering dates through imperial court diaries, temple records, and festival calendars has created one of the longest continuous biological datasets in existence, with some records from Kyoto extending back to 812 CE [@Aono2008].
